---
title: "TSA_04_21_20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load Libraries
```{r}
library("TTR")
library("forecast")
```

## Load Data
```{r}
#kings <- ts(scan("http://robjhyndman.com/tsdldata/data/kings.dat"))
births <- ts(scan("http://robjhyndman.com/tsdldata/data/nybirths.dat"), frequency = 12)
souvenir <- ts(scan("http://robjhyndman.com/tsdldata/data/fancy.dat"), frequency = 12)
rain <- ts(scan("http://robjhyndman.com/tsdldata/hurst/precip1.dat", skip = 1), frequency = 1, start = c(1813))
```

# Decompose into Parts
```{r}
plot(decompose(births))
```

# Plot 'Rain' 
```{r}
plot(rain)
```

# Holt Winters
```{r}
rainForecast <- HoltWinters(rain, beta = FALSE, gamma = FALSE)
# rainForecast$fitted # predicted values
plot(rainForecast)
```


```{r}
names(rainForecast)

```

```{r}
rainForecast$SSE
```


```{r}
forecast(rainForecast, h = 15)
```


```{r}
plot(forecast(rainForecast, h = 15))
```


```{r}
skirts <- scan("http://robjhyndman.com/tsdldata/roberts/skirts.dat",skip=5)
skirtsseries <- ts(skirts,start=c(1866))
```


```{r}
plot(skirtsseries)
```


```{r}
skirtsseriesforecasts <- HoltWinters(skirtsseries, gamma = FALSE)
skirtsseriesforecasts
```

alpha and beta are close to 1, indicating that the holt winter model favors recent numbers

```{r}
plot(skirtsseriesforecasts)
```

```{r}
plot(forecast(skirtsseriesforecasts, h = 15))
```

Fast expansion of confidence intervals when forecasting is an indication of non-stationarity

```{r}
rain2 <- forecast(rainForecast, h = 15)
acf(rain2$residuals[-1], lag.max = 20)
```

None of the residuals are correlated with eachother, so the residuals are independent, which is what we want.

```{r}
skirt2 <- forecast(skirtsseriesforecasts, h = 15)
acf(skirt2$residuals[c(-1, -2)], lag.max = 20)
```


```{r}
souvenir <- scan("http://robjhyndman.com/tsdldata/data/fancy.dat")
souvenirtimeseries <- ts(souvenir, frequency=12, start=c(1987,1))

transformedsouvenir <- log(souvenirtimeseries)

plot(transformedsouvenir)

souvenirtimeseriesforecasts <- HoltWinters(transformedsouvenir)
plot(souvenirtimeseriesforecasts)
```

```{r}
plot(forecast(souvenirtimeseriesforecasts, h = 60))
```



```{r}
s <- forecast(souvenirtimeseriesforecasts, h = 60)
acf(s$residuals[-seq(1, 12, by = 1)], lag.max = 20)
```

```{r}
qqnorm(s$residuals[-c(1:12)])
```


```{r}
library(goftest)
cvm.test(s$residuals[-c(1:12)], "pnorm")

ad.test(s$residuals[-c(1:12)], "pnorm")

hist(s$residuals[-c(1:12)])
```

```{r}

```


